\subsection{\glsentrytext{jsonld}}\label{sec:jsonldinfo}

\gls{jsonld} is the format used throughout the \gls{wot}, with its main use being \glspl{td}. It adds a semantic layer to a \gls{json} structure to let every property be a globally unique identifier -- a \gls{uri} -- based on ontologies. \gls{jsonld} provides different ways how to represent data. The most common way is to provide a so-called \enquote*{context}, so you can use more readable property names for the actual data. The context is a nested \gls{json} structure that maps the property names to the actual identifiers. \autoref{lst:example-td} shows an exemplary \gls{td} document, where the \gls{wot} ontology \cite{w3c.wot.tdo.20230111} and other secondary ontologies are referenced in its context. Some \glspl{uri} have been abbreviated for formatting reasons.

Property names use terms from a referenced context document, which provides a description and \gls{uri} for the property. Auxiliary ontologies may be referred to using a prefix. The process of getting the actual structure and identifiers is called \enquote{expansion}. Its result is a \gls{json} document where each property is a \gls{uri}. Due to the flexible nature of how to reference ontologies, two documents with the exact same semantic meaning may not have equal \gls{jsonld} representations, i.e. they're not structurally equal. Only if documents are fully expanded, they are structurally comparable (excluding arrays where the order does not matter). \autoref{lst:example-jsonld-document-expanded} shows an excerpt of the expanded example \gls{td} document from \autoref{lst:example-td}, which is -- at least seemingly -- larger, due to the \gls{uri} expansion, and deeper nested.

\begin{lstlisting}[language=json,caption={Example \gls{jsonld} document expanded},label={lst:example-jsonld-document-expanded}]
[
  {
    "@type": [
      "https://...fly.dev/ontology#TemperatureSensor"
    ],
    "@id": "https://example.com/temperature/1",
    "https://www.w3.org/2019/wot/td#title": [
      {
        "@value": "Nowhere Temperature Sensor"
      }
    ],
    ...
    "https://.../td#hasPropertyAffordance": [
      {
        "@type": [
          "https://...ntology#TemperatureAffordance",
          "https://.../wot/json-schema#NumberSchema"
        ],
        "https://.../wot/td#hasForm": [
          {
            "https://.../wot/hypermedia#hasTarget": [
              {
                "@value": "https://.../temperature"
              }
            ],
            ...
          }
        ],
        ...
      }
    ]
  }
]
\end{lstlisting}
